Testing Theories of Expectation Formation using Probabilistic Forecasts

### 2019-06-19 paper/Draft.tex
Furher's RE tests are twofold. 1. Fixing terminate date and test of revision is efficient.2.weak on testing difference in fix-horizon forecast depends on past information with coeff big enough.

Another hypothesis test of FIRE relies upon disagreements. \footnote{For instance, \cite{mankiw2003disagreement} documents substantial time-varying disagreements of inflation uses consumers and professional forecasters' survey. } As agents perfect update the same information, there is no disagreements at any point of the time.

@@

As the forecasting horizon decreases relative to a given future point of time, there is a pure efficiency gain or reduction in uncertainty as more and more shocks have realized. So the uncertainty should drop unambigously.

Quanlitatively, $\bar \sigma^2_{t+h|t+k}$ should be smaller than $\bar \sigma^2_{t+h|t}$ $\forall 1<k\leq h$.

Compared to other null hypotheses discussed above, this is a weaker test. It is true that rational forecasting relies upon utilizing all the information available at any point of time in the most efficient way.

>>>>

Another hypothesis test of FIRE relies upon disagreements. \footnote{For instance, \cite{mankiw2003disagreement} documents substantial time-varying disagreements about future inflation using consumers and professional forecasters' survey. } As agents perfect update the same information, there is no disagreements at any point of the time.

@@

As the forecasting horizon decreases relative to a given future point of time, there is a pure efficiency gain or reduction in uncertainty as more and more shocks have realized. So the uncertainty should drop unambigously. Quanlitatively, this implies that $\bar \sigma^2_{t+h|t+k} < \bar \sigma^2_{t+h|t}$ $\forall 1<k\leq h$.

Compared to other null hypotheses discussed above, this is a weaker test. It is true that rational foreacsting implies reduction in uncertainty with shorter horizon. But there is no direct test if the drop in uncertainty is efficient enough so as to be consistent with FIRE.
